paper_replication

### 2021-12-15 paper_replication.Rmd
Update paper_replication.Rmd

---
title: "paper_replication"
output: pdf_document
---
REPLICATION:
TODO: averages of averages vs. averages for table 2
TODO: possibly email Alice asking about this county vs. state table 2 issue <- Jo
TODO: write up <- Toby
TODO: find abortion data used by Brown et al. to compare in discussion <- Toby

EXTENSION:
TODO: write literature review and describe motivation for extension
TODO: figure out what is happening with the propensity scores for the extension analyses
TODO: decide whether to rescore the high vs. low restriction variable as a factor or an integer (currently coded as the latter)
TODO: add in rural vs urban and more variables do a quick variable selection

>>>>

---
title: "paper_replication"
output: pdf_document
---
REPLICATION:
TODO: averages of averages vs. averages for table 2
TODO: the paper says "all models included state and year fixed effects and standard errors adjusted for state-level clustering" -> does this mean we need to include states as a variable in our model?
TODO: the paper says "We addressed data gaps in demographic variables by using the estimate from the nearest year for which an estimate was available", so we need to include this methodology
TODO: bias analysis as done in the paper, comparing Guttmacher Census State Data to our State Data
TODO: run the models without the distance variable as well as with the distance variable as the outcome, as done in the paper
TODO: write up everything: we need to follow the format of the original paper <- Toby
TODO: find abortion data used by Brown et al. to compare in discussion <- Toby

EXTENSION:
TODO: write literature review and describe motivation for extension
TODO: figure out what is happening with the propensity scores for the extension analyses
TODO: decide whether to rescore the high vs. low restriction variable as a factor or an integer (currently coded as the latter)
TODO: add in rural vs urban variable
TODO: look at Hawkins et al paper linked in the original paper to see what mortality data they used. consider using mortality data by state.
